DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-04 rebuttal.tex

\subsection{}
\begin{mdframed}[style=comment]
One fairly significant concern I have is how convincing the application to other machine learning algorithms is. The authors compare deep sphere to a SVM classifier, in the case of distinguishing from two cosmological models from density maps. This classification is obviously a simplification of what would be done in real cosmological analyses, but is sufficient for the purpose of demonstration here. However, the metrics adopted do not clearly highlight the superiority of DeepSphere. The SVM takes pixel histograms or power spectrum densities (PSDs) of each input map. It is not surprising that DeepSphere outperforms them given that it takes the whole map as input. Histograms and PSDs are very restrictive compressions of the data - dropping a lot of spatial information. An SVM or even a standard fully connected neural network (NN) would perform a lot better. It is unclear how that would compare to DeepSphere. But I would certainly expect DeepSphere to be a lot easier to train and have many fewer parameters, which I think is the key advantage that needs to be highlighted here. This is analogous to comparing a standard convolutional NN to a standard fully-connected NN. With appropriate depth both will extract the same information and perform equally well. But of course the CNN has fewer parameters and is easier to train since its structure naturally extracts spatial information. One wouldn't compare the CNN to a SVM trained on pixel histograms or PSDs, since those would not have access to the same information. It would be more natural to compare the CNN and the NN trained on the same maps, and examine the number of parameters, the time and number of examples needed for training to achieve the same performance, etc. This would truly highlight how the structure of the NN is a key advantage.
\end{mdframed}

We agree that the ML algorithms should be tested on the same input data for a fair comparison.

We performed the comparison with these features at it reflects the two-steps traditional way in classic machine learning: a) designing features b) using a method a ``simple'' classifier. Deep learning changed this tactic with networks that learn the features directly from the raw data.
The PS and histograms were chosen because they are standard statistics used by the cosmology community for analysing real data.
This is why we chose it as the reference point.
In fact, the single step of moving away from these hand-picked statistics to ML approaches is already interesting for physicists.
It would be indeed interesting to compare the performance of the CNN to other ML-based algorithms, but we belive it is a major undertaking if to be conducted fairly.
Given that the our method gives significant advantage over the traditional statistics used in cosmology, we believe that the current scope of the paper is already interesting for cosmologists.
We would be keen to leave more detailed comparisons of ML-algorithms for future work.

@@

\begin{mdframed}[style=comment]
We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
\end{mdframed}
% \todo{Assign: @nati, @michael}
% \nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
We updated the section with a citation and some extra information.
\begin{mdframed}[style=manuscript]
We derived this rule from the Chebyshev polynomial equations and some empirical experiments. Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.
\end{mdframed}

\begin{mdframed}[style=comment]
Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
\end{mdframed}
\todo{Assign: @all}
% \nati{The problem is that random filters are picky as well and look very similar. Should we say that? I do not think a colorbar is necessary since there are numbered axes on the top plots. Do you agree?}
% \TK{Added sentence}

We decided not to add a colorbar as scale information is already present in the top plot of the figure.
We added a small explanation for the peak structure
\begin{mdframed}[style=comment]
The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
\end{mdframed}

### 2019-03-04 scnn.tex
updated radius info

The set of input pixels which influence the value of an output pixel forms a \textit{receptive field}.
That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
Its radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers if any.
Its radius should be large enough to capture statistics of interest.
For example, a partial sky observation can provide only limited information of cosmological relevance.
On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
A data and task dependent trade-off is to be found.
Note here that while global predictions use, by definition, the whole sky, dense predictions are not necessarily local.

>>>>

The set of input pixels which influence the value of an output pixel forms a \textit{receptive field}.
That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
The radius of this filter is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers, if any.
This radius should be large enough to capture statistics of interest.
For example, a partial sky observation can provide only limited information of cosmological relevance.
On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
A data and task dependent trade-off is to be found.
Note here that while global predictions use, by definition, the whole sky, dense predictions are not necessarily local.
